Adaptative neighbouring methods applied to telephonic base stations

### 2024-09-03 article.tex
adding citations

    This methods consists in multiple steps that can each be realised thanks to several methods that are compared: the $k$-NN method, the Delaunay triangulation or the Gabriel graph method are first used to create a first rough estimation of each point's neighbours. A filtering step is then applied in order to refine the neighbouring relationships that were found. This step is composed of several criteria that are successively being applied.

@@

    The field of neighbouring problems mainly revolves around the optimisation of the $k$ Nearest Neighbours ($k$-NN) algorithm.
    As indicated by its name, this method consists in considering the closest $k$ points of each points as their neighbour.
    [insert KNN reference]

    Another method consists in the using the Delaunay triangulation. Each couple of points linked by an edge in this triangulation are considered neighbours.
    [insert Delaunay neighbouring reference]

>>>>

    This methods consists in multiple steps that can each be realised thanks to several methods that are compared: the $k$-NN method, the Delaunay triangulation or the Gabriel graph method are first used to create a rough estimation of each point's neighbours. A filtering step is then applied in order to refine the neighbouring relationships that were found. This step is composed of several criteria that are successively being applied.

@@

    The field of neighbouring problems mainly revolves around the optimisation of the $k$ Nearest Neighbours ($k$-NN) algorithm.
    As indicated by its name, this method consists in considering the closest $k$ points of each points as their neighbour \cite{art_kNN}.

    Another method consists in the using the Delaunay triangulation. Each couple of points linked by an edge in this triangulation are considered neighbours \cite{MULCHRONE2003689}.
